\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{enumitem}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\urlstyle{same}

% Addressee and opening
\newcommand{\recipientInfo}[1]{
  \vspace{2em}
  Dear #1,\\
  \vspace{1.5em}
}

% Closing
\newcommand{\closing}[1]{
  \vspace{2em}
  Sincerely, \\
  \textbf{#1}
}

%\renewcommand{\paragraph}[1]{\par\noindent#1\vspace{1em}}
\renewcommand{\paragraph}[1]{\par\noindent\setlength{\parskip}{0.5em}\setlength{\parindent}{0pt}#1\par\vspace{1em}}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
%-------------------
% Cover Letter Start
%-------------------
\begin{document}

% Header
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Papop Lekhapanyaporn} & Email : \href{mailto:papop.lekhapanyaporn@gmail.com}{papop.lekhapanyaporn@gmail.com}\\
  \href{https://papop.dev}{papop.dev} & Mobile : \href{tel:+491627400833}{(+49)162-740-0833} \\
\end{tabular*}

\section{Cover letter}
% Recipient
\recipientInfo{Databricks}

% Introduction
\paragraph{
I am writing to express my interest in the Software Engineering Internship position at Databricks.
As a Bachlor student majoring in Computer Science at RWTH Aachen, expecting to graduate in October 2025, I am eager to contribute to your team and apply my skills in software development and collaborative problem-solving to create impactful solutions. 
Databricks’ mission of accelerating innovation and data-driven insights resonates strongly with me, and I am enthusiastic about the opportunity to work alongside your talented team.
}

% Body paragraph 1: Skills and experiences
\paragraph{
Long before my academic year at RWTH Aachen, I have always love to learn new things particularly about computer.
I picked Python as my first languages and later change to c/c++ for my cansat project during my 10th grade. I also picked up many languages along my coding journey and later learn java through the university course.
From the started, I have developed a strong foundation in computer science, with a particular focus on algorithms, data structures, and object-oriented programming principles. 
I am comfortable implementing efficient solutions using these languages and have consistently applied OOP principles to design scalable applications.
}

% Body paragraph 2: HPC and collaborative work
\paragraph{
In addition to my foundational knowledge, I am deeply interested in High-Performance Computing (HPC) and parallel computing. My coursework and independent studies in this area have equipped me with a keen understanding of distributed systems, parallel algorithms, and techniques to optimize computation-intensive tasks.
I am excited by the prospect of leveraging these interests to contribute to Databricks' innovative solutions, especially in optimizing data-driven workloads and scaling infrastructure.
}
% Conclusion
%
\paragraph{
Furthermore, I love to work in collaborative environments where I can work with a team to tackle ambiguous problems.
I believe my passion for finding elegant solutions through innovative thinking aligns well with Databricks’ values.
The opportunity to contribute to a culture focused on pushing the boundaries of what is possible with data would be a perfect match for my professional aspirations.
}

% Closing
\closing{Papop Lekhapanyaporn}

\end{document}

